A Data Restore Model\\ for Reproducibility in Computational Statistics

### 2013-07-03 paper-data-restore-model.Rnw
camera-ready-version, i-know 2013

\documentclass{acm_proc_article-sp}

@@

\title{
A Data Restore Model\\
for Reproducibility in Computational Statistics
}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

% A category with the (minimum) three required fields
\category{H.3.7}{Digital Libraries}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{I.2.4}{Knowledge Representation Formalisms and Methods}{Semantic networks}

\terms{Design, Algorithms, Economics}

@@

@@

The model has to make sure that individual data slices and values can be identified without ambiguity in the long term.
As we could not find an established data model for statistical data that is not subject to change and incorporates versioning at the same time, we discarded model-based queries and decided to use individual identifiers for every single value of a data set.
The number of IDs needed is certainly high and questions of scalability raise immediately.
On the other side, the IDs we are going to introduce can as well be interpreted as single-result queries or as the variables of a regular query.
%To give an estimation on the technical implications, the number of additional triples needed is twice the number of data values, or the same number only if not linked with other semantic resources.
%Maintenance could be supported with tools and there should not be any additional efforts, provided that the data is maintained in a structured representation already.
%BZ: what tools?
However, we would like to have a discussion on this na\"{\i}ve approach and leave the investigation of scalability for now.
We will introduce the concept of a \textit{data template} which is based on the idea to replace every value within a data file with its associated ID, so that the original file can be restored again simply by replacing them back with its associated values.
This could also help solve some of the problems in using linked data for scientific purposes \cite{bechhofer2010linked}\footnote{The problem of precise data references has been recognized by the Semantic Statistics community as well \url{http://datalift.org/en/event/semstats2013}.}, which will be the basis of the model.

@@

In case the researcher used own data, the data would have to be submitted to an affiliated archive\footnote{Researchers have to archive their data, either locally or at another archive. By "affiliated archive" we denote this repository.} in beforehand where the respective data template and IDs involved are generated first.
The archive returns the template to the researcher who can then publish it in the same way as described above.
This procedure must be supported with tools for mapping and ID generation.
Furthermore, these tools should provide for further semantic annotation of the content (using the RDF Data Cube Vocabulary for example) so that documentation about the data is available as well.
Figure \ref{fig:modelprocessing} outlines the overall process.

@@

\balancecolumns

>>>>

%\documentclass{acm_proc_article-sp}
\documentclass{sig-alternate}

@@

\conferenceinfo{i-Know}{'13, September 04 - 06 2013, Graz, Austria}

\CopyrightYear{2013}
\crdata{978-1-4503-2300-0/13/09}

\title{
A Data Restore Model\\
for Reproducibility in Computational Statistics
}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

% A category with the (minimum) three required fields
\category{H.3.5}{Online Information Services}{Data sharing}
\category{H.3.7}{Digital Libraries}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{I.2.4}{Knowledge Representation Formalisms and Methods}{Semantic networks}

%\category{Digital libraries and archives}

\terms{Design, Economics, Algorithms, Verification}

@@

%\newpage

@@

The model has to make sure that individual data slices and values can be identified without ambiguity in the long term.
As we could not find an established data model for statistical data that is not subject to change and incorporates versioning at the same time, we discarded model-based queries and decided to use identifiers for every single value of a data set.
The number of IDs needed is certainly high and questions of scalability raise immediately.
On the other side, the IDs we are going to introduce can as well be interpreted as single-result queries or as the variables of a regular query.
%To give an estimation on the technical implications, the number of additional triples needed is twice the number of data values, or the same number only if not linked with other semantic resources.
%Maintenance could be supported with tools and there should not be any additional efforts, provided that the data is maintained in a structured representation already.
%BZ: what tools?
However, we would like to have a discussion on this na\"{\i}ve approach and leave the investigation of scalability for now.
We will introduce the concept of a \textit{data template} which is based on the idea to replace every value within a data file with its associated ID, so that the original file can be restored again simply by replacing them back with its associated values.
This could also help solve some of the problems in using linked data for scientific purposes \cite{bechhofer2010linked}\footnote{The problem of precise data references has been recognized by the Semantic Statistics community as well \url{http://datalift.org/en/event/semstats2013}.}, which will be the basis of the model.

@@

In case the researcher used own data, the data would have to be submitted to an affiliated archive\footnote{Researchers have to archive their data, either locally or at another archive. By "affiliated archive" we denote this repository.} in beforehand where the respective data template and IDs involved are generated first.
At this point, metadata on provenance and other documentation should be collected which can be supported through scientific workflow systems\cite{cau21112}.
The archive returns the template to the researcher who can then publish it in the same way as described above.
This procedure must be supported with tools for mapping and ID generation.
Furthermore, these tools should provide for further semantic annotation of the content (using the RDF Data Cube Vocabulary for example) so that documentation about the data is available as well.
Figure \ref{fig:modelprocessing} outlines the overall process.

@@

%\balancecolumns
